TBD

### 2021-03-12 outputs/paper/paper.Rmd
updated regression for above40 rather than generic age var
need to account for fixed effects and recheck to see R^2 results - as is they're off.

### OLS formula : y = mx + c, where 
### y = response (dependent variable) - so report/no report,
### m = slope
### x = independent variable, predictor - condition (no money, money, big money)
### c = the intercept
s8_money <-
  dfBehavModel %>%
  filter(cond == 1 | cond == 2 | cond == 3)
ols_regress(response ~ cond + male + age + computer + coworkers + other_bystanders, data = s8_money)

s8_no_money <-
  dfBehavModel %>%
  filter(cond == 0)
ols_regress(response ~ cond + male + age + computer + coworkers + other_bystanders, data = s8_no_money)

>>>>

### OLS formula : y = mx + c, where 
### y = response (dependent variable) - so report/no report,
### m = slope
### x = independent variable, predictor - condition (no money, money, big money)
### c = the intercept
s8_money <-
  dfBehavModel %>%
  filter(cond == 1 | cond == 2 | cond == 3)
ols_regress(response ~ cond + male + above40 + computer + coworkers + other_bystanders, data = s8_money)

s8_no_money <-
  dfBehavModel %>%
  filter(cond == 0)
ols_regress(response ~ cond + male + above40 + computer + coworkers + other_bystanders, data = s8_no_money)
